### 2021-10-21 manuscript.Rmd
Adding balancing script
Fixed missing file

full_run <- FALSE
if (full_run) {
  source(here("analysis", "subsampling.R"))
}

@@

load(here("data/Confirmatory", "ipw_confirm.RData"))

Confirm_sim <- read.csv(here("data","Confirm_sim.csv"))
```

>>>>

full_run <- FALSE
if (full_run) {
  source(here("analysis", "balancing.R"))
}

@@

load(here("data", "Confirmatory", "ipw_confirm.RData"))

Confirm_sim <- read.csv(here("data", "Confirmatory", "Confirm_sim.csv"))
```
